Effect of metabolic state on \textit{Paraclostridium bifermentans} surface properties and the implications for lead removal

### 2021-10-05 Writeup/CET - Dead bacteria ads/reviewers_response.txt

                          REVIEWER # 1
Paper # 168
Title MICROBIAL PB(II) PRECIPITATION: THE ROLE OF BIOSOR ...........
by:Van Veenhuyzen B.,Chirwa E.,Brink H.

Scientific quality and significance of the work:..........................sufficient
Novelty & new insights into the problem:..................................good
Is the presentation clear and understandable by most readers ?:...........sufficient
Is the paper following the Template rules ?:..............................no
Is this paper referencing any Chemical Engineering Transactions article?:.yes

decision: accept after major revisions

Comments by reviewer
I suggest to address this major revisions prior its acceptance for publish:

Section 1

Modern industrial activities, such as mining and battery manufacturing, continue to introduce
lead pollutants into the environment. This results in the rapid depletion of global reserves
and the introduction of lead pollutants into the environment.

This is repetitive. Rephrase these two sentences into one.

Section 2.2

A spectrophotometer with light at 550 nm was used to measure light absorbed by solution and
infer metabolic activity from the difference between filtered and unfiltered samples

Rephrase this sentence. Suggestion: Light absorption measurements at 550 nm were performer
to infer metabolic activity differences between filtered and unfiltered samples.

Section 2.3

after 3 h exposure to 50 m NaN3
Should be: after 3 h exposure to 50 mM NaN3

Section 3.1

The appearance of new peaks could be indicative of the cell wall rupturing, resulting in the
exposure of various functional groups from the interior off the cell.

Rephrase:
The appearance of new peaks could be indicative of cell wall rupturing, resulting in the exposure
of various functional groups from cell inside.

Section 3.2, paragraph 2
Are the cited experiments performed in the same conditions of scale lead and cell concentration?
Has the process zero order kinetics with respect to lead and cell concentration. If not, consider
rephrasing the paragraph adding a notion of conversion rate instead of time to reach equilibrium.

Figure 3: consider adding error bars, change the markers for each experiment and remove lines
connecting data points.

                          REVIEWER # 2
Paper # 168
Title MICROBIAL PB(II) PRECIPITATION: THE ROLE OF BIOSOR ...........
by:Van Veenhuyzen B.,Chirwa E.,Brink H.

Scientific quality and significance of the work:..........................sufficient
Novelty & new insights into the problem:..................................sufficient
Is the presentation clear and understandable by most readers ?:...........poor
Is the paper following the Template rules ?:..............................no
Is this paper referencing any Chemical Engineering Transactions article?:.yes

decision: accept after major revisions

Comments by reviewer
The manuscript presents experimental studied on the removal of Pb using bacteria. The text
should be revised and english-proofed to make it more understandable. Also, the specific problem
that it is being tackled and the concrete objective of the work should be more clearly stated.
Finally, how can this information be applied in practical terms?

### 2021-10-25 Writeup/Catalysts/MDPI_template/template.tex
Added some introductory phrases

%=================================================================
% Full title of the paper (Capitalized)
\Title{Title}

@@

% Author Orchid ID: enter ID or remove command
\newcommand{\orcidauthorA}{0000-0000-0000-000X} % Add \orcidA{} behind the author's name
%\newcommand{\orcidauthorB}{0000-0000-0000-000X} % Add \orcidB{} behind the author's name

% Authors, for the paper (add full first names)
\Author{Brandon van Veenhuyzen $^{1,\dagger,\ddagger}$\orcidA{}, Firstname Lastname $^{1,\ddagger}$ and Firstname Lastname $^{2,}$*}

% MDPI internal command: Authors, for metadata in PDF
\AuthorNames{Brandon van Veenhuyzen, Firstname Lastname and Firstname Lastname}

% MDPI internal command: Authors, for citation in the left column
\AuthorCitation{Lastname, F.; Lastname, F.; Lastname, F.}
% If this is a Chicago style journal: Lastname, Firstname, Firstname Lastname, and Firstname Lastname.

% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
\address{%
$^{1}$ \quad Affiliation 1; e-mail@e-mail.com\\
$^{2}$ \quad Affiliation 2; e-mail@e-mail.com}

% Contact information of the corresponding author
\corres{Correspondence: e-mail@e-mail.com; Tel.: (optional; include country code; if there are multiple corresponding authors, add author initials) +xx-xxxx-xxx-xxxx (F.L.)}

% Current address and/or shared authorship
\firstnote{Current address: Affiliation 3} 
\secondnote{These authors contributed equally to this work.}
% The commands \thirdnote{} till \eighthnote{} are available for further notes

@@

@@

A consortium of bacteria has been isolated from lead-contaminated soil at a battery recycling plant in Gauteng, South Africa, that has been shown to remove Pb(II) from solution \cite{Brink2017}. This lead-resistant consortium has been the subject of many investigations in the pursuit of better understanding the removal mechanisms and possible implementations in the bioremediation and biorecovery of lead in industrial effluent. This includes studies on the influence of lead concentrations \cite{Brink2017,Peens2018d}, substrate concentration \cite{Brink2017,Brink2018}, precipitate identification \cite{Brink2019a,Peens2018}, influence of other divalent heavy metals \cite{Horstmann2020}.

@@

\cite{Chimhundi2021}
\cite{Cilliers2021}

The chemical composition of bacteria surfaces for both Gram-positive and Gram-negative bacteria are rich in negatively charged functional groups that result in an overall negative surface charge and facilitate the attraction of positively charged metal cations like ionic lead \cite{Vijayaraghavan2008}. These functional groups also allow for chemisorption to take place, where hydrogen ions are exchanged for Pb(II)
ions (Lu et al., 2012) \cite{Lu2012}.
Chemisorption not only prevents lead from entering cells, but 
Functional
group complexation can be a prominent adsorption mechanism for some bacteria
that use it to concentrate terminal electron accepting ions on the cell wall surface
\cite{Haas2001}

@@

@@

\cite{Swaren2021}
\cite{Johnson2007a}
\cite{Mera1992}
\cite{Claessens2004}
\cite{Haas2004}

>>>>

%=================================================================
% Full title of the paper (Capitalized)
\Title{Effect of metabolic state on \textit{Paraclostridium bifermentans} surface properties and the implications for lead removal}

@@

% Author Orchid ID: enter ID or remove command
\newcommand{\orcidauthorA}{0000-0002-5179-2736} % Add \orcidA{} behind the author's name
\newcommand{\orcidauthorB}{0000-0002-4699-6152} % Add \orcidB{} behind the author's name

% Authors, for the paper (add full first names)
\Author{Brandon van Veenhuyzen $^{1}$\orcidA{}, Olga Neveling $^{1}$ and Hendrik G. Brink $^{1,}$*\orcidB{}}

% MDPI internal command: Authors, for metadata in PDF
\AuthorNames{B. van Veenhuyzen, O. Neveling and H.G. Brink}

% MDPI internal command: Authors, for citation in the left column
\AuthorCitation{van Veenhuyzen, B.; Neveling, O.; Brink, H.G.}
% If this is a Chicago style journal: Lastname, Firstname, Firstname Lastname, and Firstname Lastname.

% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
\address{%
$^{1}$ \quad Water Utilisation and Environmental Engineering Division, Department of Chemical Engineering, University of Pretoria, Lynnwood Road, Hatfield, Pretoria 0002, South Africa; u15182933@tuks.co.za (B.V.); u15037780@tuks.co.za (O.N.)}

% Contact information of the corresponding author
\corres{Correspondence: deon.brink@up.ac.za}

% Current address and/or shared authorship
%\firstnote{Current address: Affiliation 3} 
%\secondnote{These authors contributed equally to this work.}
% The commands \thirdnote{} till \eighthnote{} are available for further notes

@@

Pb(II) is a highly soluble, mobile, and toxic pollutant that continues to cause a variety of human health problems. Exposure to Pb(II) can cause significant harm to most organs \cite{Tong2000}. The transformation of Pb(II) into a less mobile, insoluble precipitate greatly 
 is conventionally achieved with electrochemical treatment and chemical precipitation \cite{Fu2011}.

@@

A consortium of bacteria has been isolated from lead-contaminated soil at a battery recycling plant in Gauteng, South Africa, that has been shown to remove Pb(II) from solution \cite{Brink2017}. This lead-resistant consortium has been the subject of many investigations in the pursuit of better understanding the removal mechanisms and possible implementations in the bioremediation and biorecovery of lead in industrial effluent. This includes studies on the influence of lead concentrations \cite{Brink2017,Peens2018d}, substrate concentration \cite{Brink2017,Brink2018}, precipitate identification \cite{Brink2019a,Peens2018}, influence of other divalent heavy metals \cite{Horstmann2020}, and operation in an upward anaerobic sludge bed reactor \cite{Chimhundi2021}.

@@

\cite{Horstmann2020a} \textit{Paraclostridium bifermentans} and \textit{Klebsiella pneumoniae}

\cite{Cilliers2021}

The chemical composition of bacteria surfaces for both Gram-positive and Gram-negative bacteria are rich in negatively charged functional groups that result in an overall negative surface charge and facilitate the attraction of positively charged metal cations like ionic lead \cite{Vijayaraghavan2008}. These functional groups also allow for chemisorption to take place, where hydrogen ions are exchanged for Pb(II)
ions (Lu et al., 2012) \cite{Lu2012}.
Chemisorption not only prevents lead from entering cells, but 
Functional
group complexation can be a prominent adsorption mechanism for some bacteria
that use it to concentrate terminal electron accepting ions on the cell wall surface

\cite{Haas2001}

@@

Several authors have used acid-base titration to improve understanding of bacteria surfaces \cite{Dittrich2005} as well as using surface models to predict the effects of pH on metal binding to cell surface \cite{Daughney1998}.

Studies have also been conducted to determine effects of metabolic state on metal adsorption \cite{Mera1992,Johnson2007a}

@@

\cite{Swaren2021}

\cite{Johnson2007a}

\cite{Mera1992} Noted that

\cite{Claessens2004} Highlighted significant hysteresis and time dependence in acid-base titrations of  \textit{Shewanella putrefaciens}.

\cite{Haas2004}
